Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-11-16 paper/paper1/ms.tex
Add some prose about HPF observations

The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R, 2007PASP..119..556S} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands. We observed HAT-P-67b with HPF in-transit on 2020 April 28, 2020 May 22, and 2020 June 15 and out-of-transit on a total of \censorbox{xx} other nights.

@@

Figure \ref{fig:HPF2022campaign} shows a zoom-in on the He 10830 region of interest.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT-P-67_2022_clean.png}
    \caption{HPF spectrum of HAT-P-67 around the spring 2022 campaign.  We see conspicuous absorption during and immediately preceding the transit, but not immediately after.  The continuum normalization indices are shown by the vertical blue shaded region and the region used for computing EW is shown in the faint gray vertical band.}
    \label{fig:HPF2022campaign}
\end{figure}

>>>>

The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands. We observed HAT-P-67 with HPF on a total of 26 unique nights.  The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to about 1 hour ``tracks'', compared to conventional steerable telescopes that can conduct point-and-stare observations for hours.  We organized the observations into four campaigns to coincide with HAT-P-67b transits on 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.  These in-transit nights had 12-18 exposures per HET track, with integration times between 5-8.5 minutes.  These campaigns were designed to acquire out-of-transit observations one and two nights before and after transit, weather and schedule permitting.  These out-of-transit observations typically received 4 or fewer individual exposures.  Additionally we acquired random-in-phase observations using low priority ``P4'' time.

Finally, the observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.  The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear pristine.

@@

Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 128 observations overlaid.  We see a variability in the Helium line of up to 10\%, which is not seen in other adjacent stellar lines.  The feature width spans about 3 $\AA~$, too broad to originate from the much narrower telluric lines.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT_P_67b_He_spectrum.png}
    \caption{Overlay of all 128 individual HPF exposures of HAT-P-67, spanning 2020-2022. Variability is seen in the Helium 10833 $\AA$ band, denoted by the vertical orange shaded band, but not in the adjacent regions.  These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.  Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 $\AA$.}
    \label{fig:HPFheliumOverview}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT-P-67_2022_clean.png}
    \caption{HPF spectra of HAT-P-67 from the April/May 2022 campaign.  We see conspicuous absorption during and immediately preceding the transit, but not immediately after.}
    \label{fig:HPF2022campaign}
\end{figure}
